---
title: "Intro To R Activity"
author: "Tamana Yaqoubi"
date: "DATA 2401"
output: 
  html_document: 
    highlight: kate
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Follow each question's instructions in the code chunk below that question, if applicable. 

1. Rename this RMarkdown file in the repo folder and give it the name “RIntro_your_last_name.rmd” or something similar. Your name should be in the file name AND the author spot above. 


2. Multiply 4 by 7, then raise that to the power of 3


```{r}
num <- 4 * 7
len <- num^3
```

3. Subtract 1.5 from 10 and then raise the answer to the power of 1.3 plus 1.789

```{r}
x <- 10 - 1.50 
y <- x^(1.3+1.789)

```

4. Divide 5 by 2.5 then divide the answer by 4

```{r}
a <- 5 / 2.5 
b <- a / 4
```

5. Create an object (a variable!) called “obj1” which is the number 15

```{r}
obj1 <- 15
```

6. Create an object called “obj2”" which is the answer to the sum of 100 + 25

```{r}
obj2 <- 100 + 25
```

7. Multiply “obj1” and “obj2” together and store the answer as another object called “obj3”

```{r}
obj3 <- obj1 * obj2
``` 

8. Subtract 1 from “obj3” then calculate the 4th root of the result (raise to power of 1/4). Save this as an object called “final.answer”

```{r}
final.answer <- obj3 - 1
final.answer <- final.answer^(1/4)
```

9. Just type the variable name final.answer in the chunk below. This will print your answer to the console when you knit. 

```{r}
final.answer
```

10. Knit this file! 